# NTUTrainRL2_6
This is the lecture notes for NTU Train Course of R Project Lecture 2_6

## Shiny

### Hello Shiny!

```{r}
install.packages("shiny")
library(shiny)
runExample("01_hello")#有11個內建的範例
```

一個Shiny App會含有兩個程式:
- ui.R
- server.R

像是**Hello Shiny!**這個範例的兩個程式為:

**ui.R**

```{r}
#ui.R

shinyUI(fluidPage(

  titlePanel("Hello Shiny!"),

  sidebarLayout(
    sidebarPanel(
      sliderInput("bins",
                  "Number of bins:",
                  min = 1,
                  max = 50,
                  value = 30)
    ),

    mainPanel(
      plotOutput("distPlot")
    )
  )
))
```

**server.R**

```{r}
#server.R

shinyServer(function(input, output) {

  output$distPlot <- renderPlot({
    x    <- faithful[, 2]
    bins <- seq(min(x), max(x), length.out = input$bins + 1)

    hist(x, breaks = bins, col = 'darkgray', border = 'white')
  })
})
```

模仿一個Hello World

```{r}
setwd("C:/NTUTrainRL2")
dir.create("HelloWorld")
file.create("HelloWorld/ui.R")
file.create("HelloWorld/server.R")
```


將以下的程式碼貼入`HelloWorld/ui.R`

```{r}
# HelloWorld/ui.R

shinyUI(fluidPage(

  titlePanel("Hello World!"),

  sidebarLayout(
    sidebarPanel(
      sliderInput("bins",
                  "Number of bins:",
                  min = 5,
                  max = 30,
                  value = 15)#換最小最大與預設值
    ),

    mainPanel(
      plotOutput("distPlot")
    )
  )
))
```


將以下的程式碼貼入`HelloWorld/server.R`

```{r}
# HelloWorld/server.R

shinyServer(function(input, output) {

  output$distPlot <- renderPlot({
    x    <- faithful[, 2]
    bins <- seq(min(x), max(x), length.out = input$bins + 1)

    hist(x, breaks = bins, col = 'skyblue', border = 'white')#換fill的顏色
  })
})
```

使用`runApp()`來執行HelloWorld App

```{r}
runApp("HelloWorld")
```

### 設計使用者介面

從頭開始設計Shiny的使用者介面FirstUI。

```{r}
setwd("C:/NTUTrainRL2")
dir.create("FirstUI")
file.create("FirstUI/ui.R")
file.create("FirstUI/server.R")
```

- 使用`fluidPage()`來做一個RWD的介面
- 將以下程式碼貼入`FirstUI/ui.R`

```{r}
# FirstUI/ui.R

shinyUI(fluidPage(
  titlePanel("Title"),

  sidebarLayout(
    sidebarPanel( "Sidebar"),
    mainPanel("Main")
  )
))
```

將以下程式碼貼入`FirstUI/server.R`

```{r}
# FirstUI/server.R

shinyServer(function(input, output) {
})
```

使用`runApp()`來執行FirstUI App

```{r}
runApp("FirstUI")
```

在剛剛的範例中我們在`fluidPage()`加入了
- `titlePanel()`
- `sidebarLayout()`
  - `sidebarPanel()`
  - `mainPanel()`

我們修改一下`sidebarLayout()`的選項把`sidebarPanel()`從左邊移到右邊。

```{r}
# FirstUI/ui.R

shinyUI(fluidPage(
  titlePanel("Title"),

  sidebarLayout(position="right",
    sidebarPanel( "Sidebar"),
    mainPanel("Main")
  )
))
```

把FirstUI App再加些有的沒有的

```{r}
# FirstUI/ui.R

shinyUI(fluidPage(
  titlePanel("My StarWars App"),
  sidebarLayout(
    sidebarPanel(
      h2("Installation"),
      strong("The Force "),
      span("is available everywhere, you can install it in the usual way from your R console:"),
      code('install.packages("TheForce")'),
      br(),
      br(),
      br(),
      br(),
      img(src = "Star_Wars_Logo.png", height = 72, width = 72),
      "The Force is Strong with this one ", 
        span("Star Wars", style = "color:blue")
    ),
    mainPanel(
      h1("Introducing StarWars"),
      p("Shiny is a new package from RStudio that makes it ", 
        em("incredibly easy"), 
        " to build interactive web applications with R."),
      br(),
      p("For an introduction and live examples, visit the ",
        a("Shiny homepage.", 
          href = "http://www.rstudio.com/shiny")),
      br(),
      h2("Features"),
      p("* Build useful web applications with only a few lines of code—no JavaScript required."),
      p("* Shiny applications are automatically “live” in the same way that ", 
        strong("spreadsheets"),
        " are live. Outputs change instantly as users modify inputs, without requiring a reload of the browser.")
    )
  )
))
```

### 控制物件

### 動態輸出

### 實作

### 上傳

## Reference
* [Shiny](http://shiny.rstudio.com/)

&copy; Tony Yao-Jen Kuo 2016