# NTUTrainRL2_6
This is the lecture notes for NTU Train Course of R Project Lecture 2_6

## Shiny

### Hello Shiny!

```{r}
install.packages("shiny")
library(shiny)
runExample("01_hello")#有11個內建的範例
#runExample("02_text") # tables and data frames
#runExample("03_reactivity") # a reactive expression
#runExample("04_mpg") # global variables
#runExample("05_sliders") # slider bars
#runExample("06_tabsets") # tabbed panels
#runExample("07_widgets") # help text and submit buttons
#runExample("08_html") # Shiny app built from HTML
#runExample("09_upload") # file upload wizard
#runExample("10_download") # file download wizard
#runExample("11_timer") # an automated timer
```

一個Shiny App會含有兩個程式:
- ui.R
- server.R

像是**Hello Shiny!**這個範例的兩個程式為:

**ui.R**

```{r}
#ui.R

shinyUI(fluidPage(

  titlePanel("Hello Shiny!"),

  sidebarLayout(
    sidebarPanel(
      sliderInput("bins",
                  "Number of bins:",
                  min = 1,
                  max = 50,
                  value = 30)
    ),

    mainPanel(
      plotOutput("distPlot")
    )
  )
))
```

**server.R**

```{r}
#server.R

shinyServer(function(input, output) {

  output$distPlot <- renderPlot({
    x    <- faithful[, 2]
    bins <- seq(min(x), max(x), length.out = input$bins + 1)

    hist(x, breaks = bins, col = 'darkgray', border = 'white')
  })
})
```

模仿一個Hello World

```{r}
setwd("C:/NTUTrainRL2")
dir.create("HelloWorld")
file.create("HelloWorld/ui.R")
file.create("HelloWorld/server.R")
```


將以下的程式碼貼入`HelloWorld/ui.R`

```{r}
# HelloWorld/ui.R

shinyUI(fluidPage(

  titlePanel("Hello World!"),

  sidebarLayout(
    sidebarPanel(
      sliderInput("bins",
                  "Number of bins:",
                  min = 5,
                  max = 30,
                  value = 15)#換最小最大與預設值
    ),

    mainPanel(
      plotOutput("distPlot")
    )
  )
))
```


將以下的程式碼貼入`HelloWorld/server.R`

```{r}
# HelloWorld/server.R

shinyServer(function(input, output) {

  output$distPlot <- renderPlot({
    x    <- faithful[, 2]
    bins <- seq(min(x), max(x), length.out = input$bins + 1)

    hist(x, breaks = bins, col = 'skyblue', border = 'white')#換fill的顏色
  })
})
```

使用`runApp()`來執行HelloWorld App

```{r}
runApp("HelloWorld")
```

### 設計使用者介面

從頭開始設計Shiny的使用者介面FirstUI。

```{r}
setwd("C:/NTUTrainRL2")
dir.create("FirstUI")
file.create("FirstUI/ui.R")
file.create("FirstUI/server.R")
```

- 使用`fluidPage()`來做一個RWD的介面
- 將以下程式碼貼入`FirstUI/ui.R`

```{r}
# FirstUI/ui.R

shinyUI(fluidPage(
  titlePanel("Title"),

  sidebarLayout(
    sidebarPanel( "Sidebar"),
    mainPanel("Main")
  )
))
```

將以下程式碼貼入`FirstUI/server.R`

```{r}
# FirstUI/server.R

shinyServer(function(input, output) {
})
```

使用`runApp()`來執行FirstUI App

```{r}
runApp("FirstUI")
```

在剛剛的範例中我們在`fluidPage()`加入了
- `titlePanel()`
- `sidebarLayout()`
  - `sidebarPanel()`
  - `mainPanel()`

我們修改一下`sidebarLayout()`的選項把`sidebarPanel()`從左邊移到右邊。

```{r}
# FirstUI/ui.R

shinyUI(fluidPage(
  titlePanel("Title"),

  sidebarLayout(position="right",
    sidebarPanel( "Sidebar"),
    mainPanel("Main")
  )
))
```

使用`runApp()`來執行FirstUI App

```{r}
runApp("FirstUI")
```

把FirstUI App加些有的沒有的。

```{r}
# FirstUI/ui.R

shinyUI(fluidPage(
  titlePanel("My StarWars App"),
  sidebarLayout(
    sidebarPanel(
      h2("Installation"),
      p(strong("The Force "), "is available everywhere, you can install it in the usual way from your R console:"),
      code('install.packages("TheForce")'),
      br(),
      br(),
      br(),
      br(),
      img(src = "Star_Wars_Logo.png", height = 72, width = 72),
      "The Force is Strong with this one ", 
        span("Star Wars", style = "color:blue")
    ),
    mainPanel(
      h1("Introducing StarWars"),
      h3("Episode IV: A New Hope (1977)"),
      p("It is a period of civil war. Rebel spaceships, striking from a hidden base, have won their first victory against the evil Galactic Empire.
During the battle, Rebel spies managed to steal secret plans to the Empire's ultimate weapon, the DEATH STAR, an armored space station with enough power to destroy an entire planet.
Pursued by the Empire's sinister agents, Princess Leia races home aboard her starship, custodian of the stolen plans that can save her people and restore freedom to the galaxy...."),
      h3("Episode V: The Empire Strikes Back (1980)"),
      p("It is a dark time for the Rebellion. Although the Death Star has been destroyed, Imperial troops have driven the Rebel forces from their hidden base and pursued them across the galaxy.
Evading the dreaded Imperial Starfleet, a group of freedom fighters led by Luke Skywalker has established a new secret base on the remote ice world of Hoth.
The evil lord Darth Vader, obsessed with finding young Skywalker, has dispatched thousands of remote probes into the far reaches of space...."),
      h3("Episode VI: Return of the Jedi (1983)"),
      p("Luke Skywalker has returned to his home planet of Tatooine in an attempt to rescue his friend Han Solo from the clutches of the vile gangster Jabba the Hutt.
Little does Luke know that the GALACTIC EMPIRE has secretly begun construction on a new armored space station even more powerful than the first dreaded Death Star.
When completed, this ultimate weapon will spell certain doom for the small band of rebels struggling to restore freedom to the galaxy..."),
      h3("Episode I: The Phantom Menace (1999)"),
      p("Turmoil has engulfed the Galactic Republic. The taxation of trade routes to outlying star systems is in dispute.
Hoping to resolve the matter with a blockade of deadly battleships, the greedy Trade Federation has stopped all shipping to the small planet of Naboo.
While the Congress of the Republic endlessly debates this alarming chain of events, the Supreme Chancellor has secretly dispatched two Jedi Knights, the guardians of peace and justice in the galaxy, to settle the conflict...."),
      h3("Episode II: Attack of the Clones (2002)"),
      p("There is unrest in the Galactic Senate. Several thousand solar systems have declared their intentions to leave the Republic.
This separatist movement, under the leadership of the mysterious Count Dooku, has made it difficult for the limited number of Jedi Knights to maintain peace and order in the galaxy.
Senator Amidala, the former Queen of Naboo, is returning to the Galactic Senate to vote on the critical issue of creating an ARMY OF THE REPUBLIC to assist the overwhelmed Jedi...."),
      h3("Episode III: Revenge of the Sith (2005)"),
      p("War! The Republic is crumbling under attacks by the ruthless Sith Lord, Count Dooku. There are heroes on both sides. Evil is everywhere.
In a stunning move, the fiendish droid leader, General Grievous, has swept into the Republic capital and kidnapped Chancellor Palpatine, leader of the Galactic Senate.
As the Separatist Droid Army attempts to flee the besieged capital with their valuable hostage, two Jedi Knights lead a desperate mission to rescue the captive Chancellor...."),
      h3("Episode VII: The Force Awakens (2015)"),
      p("Luke Skywalker has vanished. In his absence, the sinister FIRST ORDER has risen from the ashes of the Empire and will not rest until Skywalker, the last Jedi, has been destroyed.
With the support of the REPUBLIC, General Leia Organa leads a brave RESISTANCE. She is desperate to find her brother Luke and gain his help in restoring peace and justice to the galaxy.
Leia has sent her most daring pilot on a secret mission to Jakku, where an old ally has discovered a clue to Luke's whereabouts....")
    )
  )
))
```

使用`runApp()`來執行FirstUI App

```{r}
runApp("FirstUI")
```

### 控制物件

控制物件是跟圖表互動的工具，讓我們用一個BasicWidgets App把所有的基本控制物件秀出來。

```{r}
setwd("C:/NTUTrainRL2")
dir.create("BasicWidgets")
file.create("BasicWidgets/ui.R")
file.create("BasicWidgets/server.R")
```

- `fluidRow()`是Boostrap的排版，用12欄平分版面
- 控制物件一覽
  - 按鈕
    - 動作按鈕`actionButton()`
    - 送出按鈕`submitButton()`
  - 勾選箱`checkboxInput()`
  - 群組勾選箱`checkboxGroupInput()`
  - 輸入日期`dateInput()`
  - 輸入日期範圍`dateRangeInput()`
  - 上傳檔案`fileInput()`
  - 提示文字`helpText()`
  - 輸入數字`numericInput()`
  - 單選鈕`radioButtons()`
  - 下拉式選單`selectInput()`
  - 滑桿`sliderInput()`
  - 輸入文字`textInput()`

每一個控制物件都有兩個選項:
- 名稱
- 標籤

將以下程式碼貼入`BasicWidgets/ui.R`

```{r}
# BasicWidgets/ui.R

shinyUI(fluidPage(
  titlePanel("Basic widgets"),
  
  fluidRow(
    
    column(3,
      h3("Buttons"),
      actionButton("action", label = "Action"),
      br(),
      br(), 
      submitButton("Submit")),
    
    column(3,
      h3("Single checkbox"),
      checkboxInput("checkbox", label = "Choice A", value = TRUE)),
    
    column(3, 
      checkboxGroupInput("checkGroup", 
        label = h3("Checkbox group"), 
        choices = list("Choice 1" = 1, 
           "Choice 2" = 2, "Choice 3" = 3),
        selected = 1)),
    
    column(3, 
      dateInput("date", 
        label = h3("Date input"), 
        value = "2014-01-01"))   
  ),
  
  fluidRow(
    
    column(3,
      dateRangeInput("dates", label = h3("Date range"))),
    
    column(3,
      fileInput("file", label = h3("File input"))),
    
    column(3, 
      h3("Help text"),
      helpText("Note: help text isn't a true widget,", 
        "but it provides an easy way to add text to",
        "accompany other widgets.")),
    
    column(3, 
      numericInput("num", 
        label = h3("Numeric input"), 
        value = 1))   
  ),
    
  fluidRow(
    
    column(3,
      radioButtons("radio", label = h3("Radio buttons"),
        choices = list("Choice 1" = 1, "Choice 2" = 2,
                       "Choice 3" = 3),selected = 1)),
    
    column(3,
      selectInput("select", label = h3("Select box"), 
        choices = list("Choice 1" = 1, "Choice 2" = 2,
                       "Choice 3" = 3), selected = 1)),
    
    column(3, 
      sliderInput("slider1", label = h3("Sliders"),
        min = 0, max = 100, value = 50),
      sliderInput("slider2", "",
        min = 0, max = 100, value = c(25, 75))
      ),
    
    column(3, 
      textInput("text", label = h3("Text input"), 
        value = "Enter text..."))   
  )

))
```

將以下程式碼貼入`BasicWidgets/server.R`

```{r}
# BasicWidgets/server.R

shinyServer(function(input, output) {
})
```

使用`runApp()`來執行BasicWidgets App

```{r}
runApp("BasicWidgets")
```

### 簡易動態輸出

做一個文字動態輸出的練習ReactiveText。

```{r}
setwd("C:/NTUTrainRL2")
dir.create("ReactiveText")
file.create("ReactiveText/ui.R")
file.create("ReactiveText/server.R")
```

在`mainPanel()`中加入2個`textOutput()`。

將以下程式碼貼入`ReactiveText/ui.R`

```{r}
# ReactiveText/ui.R

shinyUI(fluidPage(
  titlePanel("Reactive Text"),
  
  sidebarLayout(
    sidebarPanel(
      helpText("I am the King of Pirate!"),
      
      selectInput("role", 
        label = "Choose a character to display",
        choices = c("Monkey D. Luffy", "Roronoa Zoro",
          "Vinsmoke Sanji", "Tony Tony Chopper"),
        selected = "Monkey D. Luffy"),
      
      sliderInput("bounty", 
        label = "Range of bounty:",
        min = 0, max = 99999999, value = c(0, 99999999))
    ),
    
    mainPanel(
      textOutput("text1"),
      textOutput("text2")
    )
  )
))
```

將以下程式碼貼入`ReactiveText/server.R`

```{r}
# ReactiveText/server.R

shinyServer(
  function(input, output) {
  
    output$text1 <- renderText({ 
      sprintf("I am %s. And I will be the King of Pirates!", input$role)
    })
    
    output$text2 <- renderText({
      sprintf("My bounty ranges from %s to %s.", input$bounty[1], input$bounty[2])
    })
    
  }
)
```

使用`runApp()`來執行ReactiveText App

```{r}
runApp("ReactiveText")
```

### 資料集與Shiny

我們模仿在Shiny上畫一個[Wall Street Journal India](http://blogs.wsj.com/indiarealtime/2015/09/23/why-delhi-is-the-most-expensive-place-to-buy-rice-in-the-world-but-among-the-cheapest-cities-to-live-in/)的Reactive長條圖。

```{r}
setwd("C:/NTUTrainRL2")
dir.create("wsjIndia")
dir.create("wsjIndia/data")
file.create("wsjIndia/ui.R")
file.create("wsjIndia/server.R")
```

把原始資料data-CAOyC.csv複製到C:/NTUTrainRL2/wsjIndia/data目錄下之後，將以下程式碼貼入`wsjIndia/ui.R`

```{r}
# wsjIndia/ui.R

# Read dataset
dataset <- read.csv("data/data-CAOyC.csv")

# Transfer dataset into a matrix
rowName <- dataset[,1]
dataset <- dataset[,c(2:7)]
datasetMat <- data.matrix(dataset)
rownames(datasetMat) <- rowName

# Define the overall UI
shinyUI(
  # Use a fluid Bootstrap layout
  fluidPage(    
    # Give the page a title
    titlePanel("Cost of Living"),
    # Generate a row with a sidebar
    sidebarLayout(      
      # Define the sidebar with one input
      sidebarPanel(
        selectInput("dimension", "Aspects of Cost:", 
                    choices=colnames(datasetMat)),
        br(),
        helpText("Data from WSJ India.")
      ),
      # Create a spot for the barplot
      mainPanel(
        plotOutput("barPlot")  
      )
    )
  )
)
```

將以下程式碼貼入`wsjIndia/server.R`

```{r}
# wsjIndia/server.R

# Read dataset
dataset <- read.csv("data/data-CAOyC.csv")

# Transfer dataset into a matrix
rowName <- dataset[,1]
dataset <- dataset[,c(2:7)]
datasetMat <- data.matrix(dataset)
rownames(datasetMat) <- rowName

# Define a server for the Shiny app
shinyServer(function(input, output) {
  # Fill in the spot we created for a plot
  output$barPlot <- renderPlot({
    # Render a barplot
    par(las=2)
    barplot(sort(datasetMat[,input$dimension]),
            col="skyblue",
            border=NA,
            main=input$dimension,
            xlab="Hour/Minute/Dollar",
            horiz=TRUE,
            cex.names=0.6
            )
  })
})
```

使用`runApp()`來執行wsjIndia App

```{r}
runApp("wsjIndia")
```

### 上傳

## Reference
* [Shiny](http://shiny.rstudio.com/)

&copy; Tony Yao-Jen Kuo 2016